---
title: "Publications"
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| warning: false
library(fontawesome)
library(ggtext)
library(showtext)
font_add('fa-solid', 'Font Awesome 6 Free-Solid-900.otf')
font_add('fa-brands', 'Font Awesome 6 Brands-Regular-400.otf')
font_add('fa-reg', 'Font Awesome 6 Free-Regular-400.otf')
fa_path <- systemfonts::font_info(family = "Font Awesome 6 Brands Regular")[["path"]]
font_add(family = "fa-brands", regular = fa_path)

showtext_auto()
sub <- c("Data Viz", "Data Analysis", "Writing","Data Collection", "Laboratory Works", "Data Viz", "Data Analysis", "Writing","Data Collection", "Laboratory Works")
group <- c("nos","nos","nos","nos","nos","papers","papers","papers","papers","papers")
absnos <- c(15,14,13,8,3,19,19,19,19,19)
percent <- c(79,74,68,42,16,100,100,100,100,100)

library(tidyverse)
df <- data.frame(group,sub,absnos,percent)

df %>% 
    ggplot()+
    geom_segment(data = . %>% filter(group=="nos"),
         aes(x=reorder(sub,percent),xend=sub,
             y=0,yend=percent),
         size=4,color="#a984a1")+
  geom_bar(data = . %>% filter(group=="papers"), inherit.aes = TRUE,
         aes(x=sub, y=percent),fill="#84A98C",
         stat = "identity", alpha=0.3,width = 0.3)+
    geom_text(data = . %>% filter(group=="nos"),color="#2A3F3D",size=8,
        aes(x=sub,y=percent+5,
           fontface="bold",
           label=str_glue("{percent}%")
        ))+
  annotate("text",y=60,x=4.7, size=6,label="In 8 out of my 10 papers, I have contributed to Data Visualization")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf1c0;</span>",x=2, y=-3, fill=NA,label.color=NA, size=8, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf492;</span>",x=1, y=-3, fill=NA,label.color=NA, size=8, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf1ec;</span>",x=3, y=-3, fill=NA,label.color=NA, size=8, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf5a1;</span>",x=4, y=-3, fill=NA,label.color=NA, size=8, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf53f;</span>",x=5, y=-3, fill=NA,label.color=NA, size=8, color="#a984a1")+
  
ylim(0,110)+
  labs(x="", y="",
       title = "Contributions in my publications",
       caption = "DataViz by Soundarya | Total Number of Publications =19")+
    coord_flip()+
    theme_classic()+
    theme(legend.position = "none",
          plot.title = element_text(size = 28,face = "bold"),
          plot.title.position = "plot",
          plot.caption = element_text(size = 18,hjust = 0.4),
          axis.text = element_text(size = 22),
          axis.text.y  = element_text(face = "bold",color="#2A3F3D"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.line.x = element_blank(),
           axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          panel.background = element_rect(color="#EADDCA", fill="#EADDCA"),
          plot.background = element_rect(color="#EADDCA", fill="#EADDCA"))

```

## List of Publications


```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

19. Survival analysis shows tuberculosis patients with silicosis experience earlier mortality and need employer-led care models in occupational settings in India [@RupaniSurvivalanalysis2024].

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("database", fill = "#a984a1")
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

18. Obesity, Oxidative Stress, and the Moderating Role of Overcommitment: An Exploratory Analysis in Female Nurses from Western India. https://doi.org/10.31219/osf.io/2uhkf [@singh2024]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("database", fill = "#a984a1")
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

17. Sleep Quality – A Potential Link in the Relation Between Occupational Stress and Inflammation Available from: https://osf.io/65dnw [@singh2024sleepqualitypotentiala]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

16. Assessing Health Seeking Behaviors and Economic Consequences of Morbidity in Indian Construction Workers: A Multicenter Study. [@soundararajan2024]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

15. Data Management: The First Step in Reproducible Research. [@soundararajan2023datamanagementfirst]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

14. Need for workplace smoking cessation program among public transit drivers: Evidence from a cross-sectional study in a metropolitan city of Western India [@soundararajan2023]

```{r}
#| column: margin
#| layout-nrow: 2
#| echo: false
fa("database", fill = "#a984a1")
fa("vial", fill = "#a984a1")
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

13. High Craving Is Associated with Fewer Abstinent Days and Lesser Time to Relapse During Treatment in Severe Alcohol Use Disorder [@soundararajan2023a]

```{r}
#| column: margin
#| layout-nrow: 2
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

12. Validity of point-of-care device for diagnosing anemia in workers exposed to lead [@viramgami2022validitypointofcaredevice]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("database", fill = "#a984a1")

```

11. Modeling Ability to Resist Alcohol in the Human Laboratory: A Pilot Study [@sloan2022]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
```

10. Elevated Stearoyl-CoA Desaturase 1 Activity Is Associated with Alcohol-Associated Liver Disease [@klepp2022elevatedstearoylcoadesaturase]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("palette", fill = "#a984a1")
```

9.  The Motivation for Alcohol Reward: Predictors of Progressive-Ratio Intravenous Alcohol Self-Administration in Humans [@au-stangl///motivationalcoholrewarda]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

8.  FAAH and CNR1 Polymorphisms in the Endocannabinoid System and Alcohol-Related Sleep Quality [@soundararajan2021faahcnr1polymorphisms]

```{r}
#| column: margin
#| layout-nrow: 2
#| echo: false
fa("database", fill = "#a984a1")
fa("vial", fill = "#a984a1")
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

7.  Changes in DNA Methylation Persist over Time in Males with Severe Alcohol Use Disorder-a Longitudinal Follow-up Study. [@soundararajan2021changesdnamethylation]

This is my PhD publication which had a very long incubation. However, this inspired me to visualize and I created a timeline for publishing this work [here](https://github.com/soundarya24/MyRSpace/blob/main/My%20Thesis%20Manuscript%20Timeline/ThesisTimeline.png)

This publication gathered media attention as well. The write-up in "The Hindu" - one of the eminent dailies in India can be accessed [here](https://www.thehindu.com/news/national/karnataka/excess-alcohol-intake-can-irreversibly-change-dna-nimhans-study/article33826963.ece)

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("database", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

6.  Docosahexaenoic Acid Supplementation in Age-Related Cognitive Decline: A Systematic Review and Meta-Analysis [@balachandar2020docosahexaenoicacidsupplementation]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

5.  Relation Between Age at First Alcohol Drink & Adult Life Drinking Patterns in Alcohol-Dependent Patients [@soundararajan2017relationagefirst]

I created graphs for this publication with excel back in 2015. However, after learning R, I upgraded the visualization for this paper. My twitter link for the same is [here](https://twitter.com/SoundaryaRak/status/1529423882821595136?s=20&t=iG_mmXYISfw5J6QBRwZs2A).

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

4.  Personality Profile and Short-Term Treatment Outcome in Patients with Alcohol Dependence: A Study from South India [@soundararajan2017personalityprofileshortterm]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("vial", fill = "#a984a1")
```

3.  Manganese- and 1-Methyl-4-Phenylpyridinium-Induced Neurotoxicity Display Differences in Morphological, Electrophysiological and Genome-Wide Alterations: Implications for Idiopathic Parkinson's Disease [@mythri2017manganese1methyl4phenylpyridiniuminducedneurotoxicity]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("database", fill = "#a984a1")
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

2.  Vitamin B12 Deficiency: An Important Reversible Co-Morbidity in Neuropsychiatric Manifestations. [@issac2015vitaminb12deficiency]

This is my most-cited paper.

I also visualized how this paper boosted my citation count. View it [here](https://ss-myrspace.netlify.app/posts/2022-04-06-my-scholar-profile-visualization/)

1.  Services for Enhanced Recovery with Intensive and Continued Engagement (SERWICE): An Outpatient Psychiatric Rehabilitation Model from India [@sivakumar2014servicesenhancedrecovery].

::: column-margin
`r fa("database", fill = "#a984a1")`
:::
