---
title: "Publications"
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| warning: false
library(fontawesome)
library(ggtext)
library(showtext)
font_add('fa-solid', 'Font Awesome 6 Free-Solid-900.otf')
font_add('fa-brands', 'Font Awesome 6 Brands-Regular-400.otf')
font_add('fa-reg', 'Font Awesome 6 Free-Regular-400.otf')
fa_path <- systemfonts::font_info(family = "Font Awesome 6 Brands Regular")[["path"]]
font_add(family = "fa-brands", regular = fa_path)

showtext_auto()
sub <- c("Data Viz", "Data Analysis", "Writing","Data Collection", "Laboratory Works", "Data Viz", "Data Analysis", "Writing","Data Collection", "Laboratory Works")
group <- c("nos","nos","nos","nos","nos","papers","papers","papers","papers","papers")
absnos <- c(7,6,6,4,2,10,10,10,10,10)
percent <- c(70,60,60,40,20,100,100,100,100,100)

library(tidyverse)
df <- data.frame(group,sub,absnos,percent)

df %>% 
    ggplot()+
    geom_segment(data = . %>% filter(group=="nos"),
         aes(x=reorder(sub,percent),xend=sub,
             y=0,yend=percent),
         size=4,color="#a984a1")+
  geom_bar(data = . %>% filter(group=="papers"), inherit.aes = TRUE,
         aes(x=sub, y=percent),fill="#84A98C",
         stat = "identity", alpha=0.3,width = 0.3)+
    geom_text(data = . %>% filter(group=="nos"),color="#2A3F3D",
        aes(x=sub,y=percent+5,
           fontface="bold",
           label=str_glue("{percent}%")
        ))+
  annotate("text",y=60,x=4.7, label="In 70% of my papers, I have contributed to Data Visualization")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf1c0;</span>",x=2, y=105, fill=NA,label.color=NA, size=5, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf492;</span>",x=1, y=105, fill=NA,label.color=NA, size=5, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf1ec;</span>",x=3, y=105, fill=NA,label.color=NA, size=5, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf5a1;</span>",x=4, y=105, fill=NA,label.color=NA, size=5, color="#a984a1")+
  geom_richtext(label="<span style='font-family:fa-solid;'>&#xf53f;</span>",x=5, y=105, fill=NA,label.color=NA, size=5, color="#a984a1")+
  
ylim(0,110)+
  labs(x="", y="",
       title = "Contributions in my publications",
       caption = "DataViz by Soundarya | Total Number of Publications =10")+
    coord_flip()+
    theme_classic()+
    theme(legend.position = "none",
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.line.x = element_blank(),
           axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          panel.background = element_rect(color="#EADDCA", fill="#EADDCA"),
          plot.background = element_rect(color="#EADDCA", fill="#EADDCA"))

```

## List of Publications

1.  Services for Enhanced Recovery with Intensive and Continued Engagement (SERWICE): An Outpatient Psychiatric Rehabilitation Model from India [@sivakumar2014servicesenhancedrecovery].


::: column-margin
`r fa("database", fill = "#a984a1")`
:::

2.  Vitamin B12 Deficiency: An Important Reversible Co-Morbidity in Neuropsychiatric Manifestations. [@issac2015vitaminb12deficiency]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("database", fill = "#a984a1")
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

This is one of my most-cited papers.

I also visualized how this paper boosted my citation count. View it [here](https://ss-myrspace.netlify.app/posts/2022-04-06-my-scholar-profile-visualization/)

3.  Manganese- and 1-Methyl-4-Phenylpyridinium-Induced Neurotoxicity Display Differences in Morphological, Electrophysiological and Genome-Wide Alterations: Implications for Idiopathic Parkinson's Disease [@mythri2017manganese1methyl4phenylpyridiniuminducedneurotoxicity]

::: column-margin
`r fa("vial", fill = "#a984a1")`
:::

4.  Personality Profile and Short-Term Treatment Outcome in Patients with Alcohol Dependence: A Study from South India [@soundararajan2017personalityprofileshortterm]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

5.  Relation Between Age at First Alcohol Drink & Adult Life Drinking Patterns in Alcohol-Dependent Patients [@soundararajan2017relationagefirst]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

This was another exciting work. I also happened to redo the visualization pertaining to this paper. New data viz can be visualized [here](https://twitter.com/SoundaryaRak/status/1529423882821595136?s=20&t=iG_mmXYISfw5J6QBRwZs2A).

6.  Docosahexaenoic Acid Supplementation in Age-Related Cognitive Decline: A Systematic Review and Meta-Analysis [@balachandar2020docosahexaenoicacidsupplementation]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("database", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

7.  Changes in DNA Methylation Persist over Time in Males with Severe Alcohol Use Disorder-a Longitudinal Follow-up Study. [@soundararajan2021changesdnamethylation]

```{r}
#| column: margin
#| layout-ncol: 2
#| echo: false
fa("database", fill = "#a984a1")
fa("vial", fill = "#a984a1")
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

I made a timeline for publishing this work [here](https://github.com/soundarya24/MyRSpace/blob/main/My%20Thesis%20Manuscript%20Timeline/ThesisTimeline.png)

This publication gathered media attention as well. The write-up in a daily can be accessed [here](https://www.thehindu.com/news/national/karnataka/excess-alcohol-intake-can-irreversibly-change-dna-nimhans-study/article33826963.ece)

8.  FAAH and CNR1 Polymorphisms in the Endocannabinoid System and Alcohol-Related Sleep Quality [@soundararajan2021faahcnr1polymorphisms]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
fa("marker", fill = "#a984a1")
```

9.  The Motivation for Alcohol Reward: Predictors of Progressive-Ratio Intravenous Alcohol Self-Administration in Humans [@au-stangl///motivationalcoholrewarda]

::: column-margin
`r fa("palette", fill = "#a984a1")`
:::

10. Elevated Stearoyl-CoA Desaturase 1 Activity Is Associated with Alcohol-Associated Liver Disease [@klepp2022elevatedstearoylcoadesaturase]

```{r}
#| column: margin
#| layout-nrow: 1
#| echo: false
fa("calculator", fill = "#a984a1")
fa("palette", fill = "#a984a1")
```